What We Eval in the Shadows

### 2021-08-10 paper/main.tex
Update discussion in 5.1

\paragraph{Consistency} It is interesting how many different forms any given
site sees. The more forms, the harder it is to characterize behavior at that
site. Luckily, \packageNbOneMinimizedPercent of sites only see a single form.
In other words, a compiler could correctly predict the \emph{shape} of an
expression by looking just at the first call in \packageNbOneMinimizedPercent
of the sites. Few sites are highly polymorphic (8 or more different forms).
These include the pipe operator of the \c{magrittr} package, used to compose
functions, \eg instead of \c{f(g(h(x),y),z)} one can write \c{h(x) \%>\% g(y) \%>\%
f(z)}.

\paragraph{Discussion} The variety of uses of \eval is evidenced by the number
of different forms. In comparison, JavaScript \eval usage was more
straightforward and more predictable as reported by \citet{oopsla12b}, with
98.7\% of the sites with only one form. Nevertheless, simple forms dominate
in R. Among these there are many cases where \eval could be replaced by less
powerful constructs such as \c{get} to lookup a name in an environment,
\c{assign} to set a value to a name in an environment or \c{call} to
reflectively call a function.
% TODO: how many receive just the simple form

>>>>

It is interesting how many different forms any given site sees. The more forms,
the harder it is to characterize behavior at that site. Luckily,
\packageNbOneMinimizedPercent of sites only see a single form. In other words,
a compiler could correctly predict the \emph{shape} of an expression by looking
just at the first call in \packageNbOneMinimizedPercent of the sites. Few sites
are highly polymorphic (8 or more different forms). These include the pipe
operator of the \c{magrittr} package, used to compose functions, \eg instead of
\c{f(g(h(x),y),z)} one can write \c{h(x) \%>\% g(y) \%>\% f(z)}.

The variety of uses of \eval is evidenced by the number of different forms. In
comparison, JavaScript \eval usage was more straightforward and more
predictable as reported by \citet{oopsla12b}, with 98.7\% of the sites with
only one form. On the other hand, there are \packageNbSimpleMinimizedOne sites
that only receive one of the simple forms (\ie\xspace \c{X}, \c{V}, \c{\$} or
\c{<-}). Additional \packageNbSimpleMinimizedMore sites takes multiple forms,
but all are these simple ones. Among these sites there are many cases where
\eval could be replaced by less powerful constructs such as \c{get} to lookup a
name in an environment, \c{assign} to set a value to a name in an environment
or \c{do.call} to reflectively call a function.
